---
title: "Final_Project_Script"
author: "Hans Kristian Erik Bruun Mortensen"
date: "2023-12-10"
output: html_document
---

Starting with installing the necessary packages

```{r}
library(tidyverse)
library(ggplot2)
```

Then i import my datasets into R

```{r}
China_Military_Personel <- read_csv2("Data_FP/China_Military_Personel.csv")
USA_Military_Personel <- read_csv2("Data_FP/USA_Military_Personel.csv")
China_MilitaryGDP <- read_csv2("Data_FP/China_MilitaryGDP.csv")
USA_MilitaryGDP <- read_csv2("Data_FP/USA_MilitaryGDP.csv")
China_Nuclear_Stockpile_Development <- read_csv2("Data_FP/China_Nuclear_Stockpile_Development.csv")
China_Nuclear_Stockpile <- read_csv2("Data_FP/China_Nuclear_Stockpile.csv")
USA_Nuclear_Stockpile <- read_csv2("Data_FP/USA_Nuclear_Stockpile.csv")
USA_Nuclear_Stockpile_Development <- read_csv2("Data_FP/USA_Nuclear_Stockpile_Development.csv")
Nations_With_Nuclear_Weapons <- read_csv2("Data_FP/Nations_With_Nuclear_Weapons.csv")

```
Now i want to inspect my data by using the str() function, so i can get an overview of how R reads my data

```{r}
str(China_Military_Personel)
str(China_MilitaryGDP)
str(USA_MilitaryGDP)
str(China_Nuclear_Stockpile_Development)
str(China_Nuclear_Stockpile)
str(USA_Nuclear_Stockpile)
str(USA_Nuclear_Stockpile_Development)
```

I can see that it reads my data correctly

### my data 

###Development in chinese and american military personal

Now i going to plot my data with ggplot, starting with the development in chinese military personel since 1978 

```{r}
ggplot(data = China_Military_Personel)+
  geom_line(mapping = aes(x = Year, y = Military_Personel))+
  labs(title = "Chinese military personel", y = "Military personel", x = "year")
```
Next up i want to make vizualise the american military personel since 1978

```{r}
ggplot(data = USA_Military_Personel)+
  geom_line(mapping = aes(x = Year, y = Military_Personel))+
  labs(title = "USA military personel")
  
```
###Development in chinese and american military expenditure as a share of GDP

In the following section i am going to visualize the procentage of GDP spend on military by each nation.Starting with China

```{r}
ggplot(data = China_MilitaryGDP)+
  geom_line(mapping = aes(x = Year, y = Percentages_of_GDP, color = "red"))+
  labs(title = "China military expenses as a share of GDP since 1989", x = "Year", y = "Percentages of GDP")
  

```
And then USA

```{r}
ggplot(data = USA_MilitaryGDP)+
  geom_line(mapping = aes(x = Year, y = Percentages_of_GDP))+
  labs(title = "USA military expenses as a share of GDP since 1989", x = "year", y = "Percentages of GDP")
```

To create a better visualization i am going to merge the two graphs.

```{r}
ggplot()+
  geom_line(data = USA_MilitaryGDP, mapping = aes(x = Year, y = Percentages_of_GDP, color = "USA"))+
  geom_line(data = China_MilitaryGDP, mapping = aes(x = Year, y = Percentages_of_GDP, color = "China"))+
  labs(x = "year", y = "Percentages of GDP", title = "China and USA combined ")
```







###Chinese and american possesion of nuclear weapons

In this section i want to showcase the development in the amount of nuclear weapons each nations has possessed since 1978. Starting with China.

```{r}
ggplot(data = China_Nuclear_Stockpile_Development)+
  geom_col(mapping = aes(x =Year, y = China_Nuclear_Stockpile_Development$`Nuclear_weapons-stockpile`, color = "red"))+
  labs( y = "Nuclear weapon stockpile", x = "Year", title ="Chinas inventory of Nuclear weapons since 1978")
```

And now the United States.

```{r}
ggplot(mapping = aes(x = USA_Nuclear_Stockpile_Development$Year, y = USA_Nuclear_Stockpile_Development$Nuclear_weapon_stockpile))+
  geom_col(colour = "blue")+
  labs(x = "Year", y = "Nuclear weapon stockpile", title = "USA nuclear stockpile development")


  
```


#Chinese and american possesion of nuclear weapons compared to the rest of the nations in possesion of nuclear weapons.

In this final section i am going to compare the 9 nations which possesses nuclear weapons.

```{r}
ggplot(data = Nations_With_Nuclear_Weapons)+
  geom_col(mapping = aes(x = Nations_With_Nuclear_Weapons$Nation, y = Nations_With_Nuclear_Weapons$Nuclear_Weapon_Stocpile, colour = Nations_With_Nuclear_Weapons$Nation))+
  labs(x = "Nation", y = "Nuclear weapon stockpile")
```


