---
title: "LEAFLET_HOME_WORK"
author: "Hans Kristian Erik Bruun Mortensen"
date: "2023-10-09"
output: html_document
---

## CREATE INTERACTIVE MAP IN R

# # Task 1: Create a Danish equivalent of AUSmap with esri layers, but call it DANmap

Starting with installing the necessary packages

````{r}
library(leaflet)
library(htmlwidgets)
library(tidyverse)
```

```{r}
library(googlesheets4)
```

Then i add the coordinates of Denmark, using the coordinates off Copenhagen due to its placement relative central placement if you consider Bornholm as a part of DK. 

```{r}
leaflet() %>% 
  setView(13.197304, 55.719437, zoom = 6) %>% 
  addTiles()
```
Now i am adding the ESRI layers to the map

```{r}
esri <- grep("^Esri", providers, value = TRUE)
```

Afterwards i am defining the DK coordinates 

```{r}
DK_KOORDINATOR <- leaflet() %>% 
  setView(13.197304, 55.719437, zoom = 6)
```

Adding mapbaggrounds to the DK-map with the following function:

```{r}
for (provider in esri) {
  DK_KOORDINATOR <- DK_KOORDINATOR %>% addProviderTiles(provider, group = provider)
}
```

Now i can add the DK-map and use the "addMeasure" function

```{r}
DANmap <- DK_KOORDINATOR %>%
  addLayersControl(baseGroups = names(esri),
                   options = layersControlOptions(collapsed = FALSE)) %>%
  addMiniMap(tiles = esri[[1]], toggleDisplay = TRUE,
             position = "bottomright") %>%
  addMeasure(
    position = "bottomleft",
    primaryLengthUnit = "meters",
    primaryAreaUnit = "sqmeters",
    activeColor = "#3D535D",
    completedColor = "#7D4479") %>% 
  htmlwidgets::onRender("
                        function(el, x) {
                        var myMap = this;
                        myMap.on('baselayerchange',
                        function (e) {
                        myMap.minimap.changeLayer(L.tileLayer.provider(e.name));
                        })
                        }") %>% 
addControl("", position = "topright")

DANmap
          
```

Saving the map

```{r}
saveWidget(DANmap, "DANmap.html", selfcontained = TRUE)
```


# Task 2: Read in the googlesheet data you and your colleagues populated with data into the DANmap object you created in Task 1.

Placing the coordinates in to the map

```{r}
spots_dk <- read_sheet("https://docs.google.com/spreadsheets/d/1PlxsPElZML8LZKyXbqdAYeQCDIvDps2McZx1cTVWSzI/edit#gid=500762785", col_types = "cccnncnc", range = "DigitalMethods")
```
```{r}
glimpse(spots_dk)
```
Putting the data in the map

```{r}
DANmap_sheetdata <- DK_KOORDINATOR %>% 
  addLayersControl(baseGroups = names(esri),
                   options = layersControlOptions(collapsed = FALSE)) %>%
  addMiniMap(tiles = esri[[1]], toggleDisplay = TRUE,
             position = "bottomright") %>%
  addMeasure(
    position = "bottomleft",
    primaryLengthUnit = "meters",
    primaryAreaUnit = "sqmeters",
    activeColor = "#3D535D",
    completedColor = "#7D4479") %>% 
  htmlwidgets::onRender("
                        function(el, x) {
                        var myMap = this;
                        myMap.on('baselayerchange',
                        function (e) {
                        myMap.minimap.changeLayer(L.tileLayer.provider(e.name));
                        })
                        }") %>% 
  addControl("", position = "topright") %>% 
  addMarkers(lng = spots_dk$Longitude, 
             lat = spots_dk$Latitude,
             popup = spots_dk$Description) 
  
```
```{r}
DANmap_sheetdata
```

## Task 3: Can you cluster the points in Leaflet? Google "clustering options in Leaflet"

The points can be clustered by using the "clusterOptions = markerClusterOptions" function, in "addMarkers"

```{r}
DANmap_sheetdata_cluster <- DK_KOORDINATOR %>% 
  addLayersControl(baseGroups = names(esri),
                   options = layersControlOptions(collapsed = FALSE)) %>%
  addMiniMap(tiles = esri[[1]], toggleDisplay = TRUE,
             position = "bottomright") %>%
  addMeasure(
    position = "bottomleft",
    primaryLengthUnit = "meters",
    primaryAreaUnit = "sqmeters",
    activeColor = "#3D535D",
    completedColor = "#7D4479") %>% 
  htmlwidgets::onRender("
                        function(el, x) {
                        var myMap = this;
                        myMap.on('baselayerchange',
                        function (e) {
                        myMap.minimap.changeLayer(L.tileLayer.provider(e.name));
                        })
                        }") %>% 
  addControl("", position = "topright") %>% 
  addMarkers(lng = spots_dk$Longitude, 
             lat = spots_dk$Latitude,
             popup = spots_dk$Description,
             clusterOptions = markerClusterOptions)
```
```{r}
DANmap_sheetdata_cluster
```

## TASK 4 -  Look at the map and consider what it is good for and what not.

A good things is on the map it is easy to find and click on the different points, where you can see some of the described information from the Google Sheets. What is not working well is when you click on the different points, it does not give all the information that is included in the Google Sheets

## TASK 5 - Find out how to display notes and classifications in the map.

We will try to add the rest of the information from the Google Sheets.


```{r}
DANMap_sheets_allinfo <- DK_KOORDINATOR %>% 
  addLayersControl(baseGroups = names(esri),
                   options = layersControlOptions(collapsed = FALSE)) %>%
  addMiniMap(tiles = esri[[1]], toggleDisplay = TRUE,
             position = "bottomright") %>%
  addMeasure(
    position = "bottomleft",
    primaryLengthUnit = "meters",
    primaryAreaUnit = "sqmeters",
    activeColor = "#3D535D",
    completedColor = "#7D4479") %>% 
  htmlwidgets::onRender("
    function(el, x) {
                        var myMap = this;
                        myMap.on('baselayerchange',
                        function (e) {
                        myMap.minimap.changeLayer(L.tileLayer.provider(e.name));
                        })
                        }") %>% 
  addControl("", position = "topright") %>% 
        addMarkers(lng = spots_dk$Longitude,
                        lat = spots_dk$Latitude,
                        popup = paste0( "<b>Name: </b>",spots_dk$Placename,
                        "<br>","<b>Type: </b>",
                        spots_dk$Type,"<br>",
                        "<b>Description: </b>",
                        spots_dk$Description,"<br>","<b>Stars 1-5: </b>",spots_dk$Stars1_5), clusterOptions = markerClusterOptions)
```
```{r}
DANMap_sheets_allinfo
```






